---
title: "chattrScript"
author: "Katiana Estrada"
output: html_document
date: "2023-06-01"
---

```{r chunk1, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## clear environment
rm(list = ls())
```

Load in necessary libraries and chattr scripts

```{r chunk2, include=TRUE}
## install rlena package from GitHub - needed first time you run code
#devtools::install_github("HomeBankCode/rlena", dependencies = TRUE)

## load packages
library("rlena")
library("readxl")
library("writexl")
library("tidyverse")

## load in functions from base chattr scripts
source("/Users/dominic/Desktop/ISL/chattrProcessing/chattrScripts/chattr-helpers.R")
source("/Users/dominic/Desktop/ISL/chattrProcessing/chattrScripts/continuation-detectors.R") 
source("/Users/dominic/Desktop/ISL/chattrProcessing/chattrScripts/estimate-baseline.R")
source("/Users/dominic/Desktop/ISL/chattrProcessing/chattrScripts/fetch-chattr-info.R")
source("/Users/dominic/Desktop/ISL/chattrProcessing/chattrScripts/intseq-detectors.R")
source("/Users/dominic/Desktop/ISL/chattrProcessing/chattrScripts/make-summaries.R")
source("/Users/dominic/Desktop/ISL/chattrProcessing/chattrScripts/tabularize-data.R") 
source("/Users/dominic/Desktop/ISL/chattrProcessing/chattrScripts/transition-detectors.R")
```

## Convert .its File to .txt File Using rlena Package

```{r chunk3, include=TRUE}
## reads in first .its file 
files <- list.files(path="/Users/dominic/Desktop/ISL/chattrProcessing/Data/current", pattern="*.its", full.names=TRUE, recursive=FALSE)
for (x in files) {
sampIts <- read_its_file(x)

## gathers all vocalizations
segments <- gather_segments(sampIts)

## select subet of segments needed for chattr scripts
segments <- segments[,c("spkr", "startTime", "endTime")]

## rename columns for chattr script to run properly
segments <- segments %>%
  rename(speaker = spkr) %>%
  rename(start.ms = startTime) %>%
  rename(stop.ms = endTime)

## convert s to ms for chattr script to run properly
segments$start.ms <- 1000 * (segments$start.ms)
segments$stop.ms <- 1000 * (segments$stop.ms)

## save .txt file into Data folder
write.table(segments, file = "/Users/dominic/Desktop/ISL/chattrProcessing/Data/txt Files/Racheltxt/rachel.txt", sep = "\t", 
            row.names = FALSE, col.names = FALSE)
}
```

## chattr Processing

fetch_chatter_BST --> function for tabular format data; needs .txt file in "expected format" specified on GitHub page
fetch_chatter_LENA --> function for .its files 
target.ptcp --> target participant - set to child wearing recorder "CHN"
interactants --> caregivers, specifically male adult near (MAN) and female adult near (FAN) - "^[MF]AN"
allowed.gap --> the maximum amount of time, in milliseconds, that is allowed to pass during a speaker transition - set to 5000ms

```{r chunk4, include=TRUE}
## loads in .its file and calculates turn transitions between target participant and specified interactants
sampFetch <- fetch_chatter_BST("/Users/dominic/Desktop/ISL/chattrProcessing/Data/txt Files/FXS/20190819_210318_025481_2.txt", 
                                target.ptcp = "CHN", interactants = "^[MF]AN",
                               allowed.gap = 5000)

## pulls table that contains the detailed turn taking data detected by chattr, including both turn transitions and interactional sequences
sampOut <- sampFetch$real.tt.vals

## create column with participant .its file name for later merging with assessmentID
sampOut['its File']='20190819_210318_025481_2.its'

## save chattr .xlsx file
write_xlsx(sampOut, "/Users/dominic/Desktop/ISL/chattrProcessing/Data/chattr Output/chattr_output_05_31_23.xlsx")
```


